Estimating R Anxiety Level Distribution Among Students At the University Using MRP

### 2020-12-22 outputs/paper/paper.Rmd
rmd fixed

```{r setup, include=FALSE}
#hide code from pdf outputs
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
#load libraries that I am going to use
library(tidyverse)
library(readr)
library(brms)
library(tidybayes)
library(ggplot2)
library(forcats)
library(ggpubr)#to put ggplots into a matrix
```

@@

  We get our post-stratification estimates by equation (1), where $J_s$ are all the cells that are in the subpopulation and  $\hat{y}_{sub}^{PS}$ is based on our multilevel regression model.
You can see that the key to an accurate estimate relies not only on how well the model fits the data but also on the level to which the census represents the population.

@@

```{r, echo = FALSE, include=FALSE}
# Run Model
mod1 <- brms::brm(
  anxiety_score ~ (1|sex) + (1|program) + (1|cgpa) + (1|coding_exp),
  data = clean_data,
  control = list(adapt_delta = 0.99)
)
```

@@

#Plot our MRP estimates 
res_sex %>% 
  ggplot(aes(y = mean, x = fct_inorder(sex), color= "MRP estimate")) + #Plot the prediction results
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +#Add error bars
  geom_point(data = clean_data %>% #Add raw data average
               group_by(sex) %>% 
               summarise(total = sum(anxiety_score), n =n()) %>% 
               mutate(avg = total/n),
             aes(sex, avg, color = "Raw Survey Data")
             )+
  theme_light()+
  xlab("Sex")+ ylab("Anxiety Score")
```

```{r, fig.cap="MRP estimates vs Raw data in different programs",fig.height=4, fig.width=7}
program_prop <- read_csv("~/Downloads/STA304-PS5-master/inputs/data/program_prop.csv")
res_program <- mod1 %>% 
  add_predicted_draws(newdata = program_prop, allow_new_levels = TRUE) %>% 
  rename(anxiety_predict = .prediction) %>% 
  mutate(anxiety_predict_prop = anxiety_predict*prop) %>% 
  group_by(program, .draw) %>% 
  summarise(anxiety_predict = sum(anxiety_predict_prop)) %>% 
  group_by(program) %>% 
  summarise(
    mean = mean(anxiety_predict),
    lower = quantile(anxiety_predict, 0.025),
    upper = quantile(anxiety_predict, 0.975)
  )

res_program %>% 
  ggplot(aes(y = mean, x = fct_inorder(program), color= "MRP estimate")) + 
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  geom_point(data = clean_data %>% 
               group_by(program) %>% 
               summarise(total = sum(anxiety_score), n =n()) %>% 
               mutate(avg = total/n),
             aes(program, avg, color = "Raw Survey Data")
             )+
  theme_light()+
  xlab("Program")+ ylab("Anxiety Score")+
    coord_flip()
```

@@

res_cgpa %>% 
  ggplot(aes(y = mean, x = fct_inorder(cgpa), color= "MRP estimate")) + 
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  geom_point(data = clean_data %>% 
               group_by(cgpa) %>% 
               summarise(total = sum(anxiety_score), n =n()) %>% 
               mutate(avg = total/n),
             aes(cgpa, avg, color = "Raw Survey Data")
             )+
  theme_light()+
  xlab("cgpa")+ ylab("Anxiety Score")+
  coord_flip()
```

@@

res_code %>% 
  ggplot(aes(y = mean, x = fct_inorder(coding_exp), color= "MRP estimate")) + 
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  geom_point(data = clean_data %>% 
               group_by(coding_exp) %>% 
               summarise(total = sum(anxiety_score), n =n()) %>% 
               mutate(avg = total/n),
             aes(coding_exp, avg, color = "Raw Survey Data")
             )+
  theme_light()+
  xlab("Coding Experience")+ ylab("Anxiety Score")
```

@@

# Appendix

>>>>

```{r setup, include=FALSE}
#hide code from pdf outputs
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)#load libraries that I am going to use
library(tidyverse)
library(readr)
library(brms)
library(tidybayes)
library(ggplot2)
library(forcats)
library(ggpubr)#to put ggplots into a matrix
```

@@

We get our post-stratification estimates by equation (1), where $J_s$ are all the cells that are in the subpopulation and  $\hat{y}_{sub}^{PS}$ is based on our multilevel regression model.

You can see that the key to an accurate estimate relies not only on how well the model fits the data but also on the level to which the census represents the population.

@@

```{r, echo = FALSE, include = FALSE}
# Run Model
mod1 <- brms::brm(
  anxiety_score ~ (1|sex) + (1|program) + (1|cgpa) + (1|coding_exp),
  data = clean_data,
  control = list(adapt_delta = 0.99)
)
```

@@

#Plot our MRP estimates 
res_sex %>% 
ggplot(aes(y = mean, x = fct_inorder(sex), color= "MRP estimate")) + #Plot the prediction results
  geom_point() +
geom_errorbar(aes(ymin = lower, ymax = upper)) +#Add error bars
  geom_point(data = clean_data %>% 
               group_by(sex) %>% 
               summarise(total = sum(anxiety_score), n =n()) %>%                
               mutate(avg = total/n),
             aes(sex, avg, color = "Raw Survey Data")#Display the raw data for comparison
             ) +
  theme_light()+
  xlab("Sex")+ ylab("Anxiety Score")
```

```{r, fig.cap="MRP estimates vs Raw data in different programs", fig.height=4, fig.width=7}
program_prop <- read_csv("~/Downloads/STA304-PS5-master/inputs/data/program_prop.csv")
res_program <- mod1 %>% 
  add_predicted_draws(newdata = program_prop, allow_new_levels = TRUE) %>% 
  rename(anxiety_predict = .prediction) %>% 
  mutate(anxiety_predict_prop = anxiety_predict*prop) %>% 
  group_by(program, .draw) %>% 
  summarise(anxiety_predict = sum(anxiety_predict_prop)) %>% 
  group_by(program) %>% 
  summarise(
    mean = mean(anxiety_predict),
    lower = quantile(anxiety_predict, 0.025),
    upper = quantile(anxiety_predict, 0.975)
  )

res_program %>% 
  ggplot(aes(y = mean, x = fct_inorder(program), color= "MRP estimate")) + 
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  geom_point(data = clean_data %>% 
               group_by(program) %>% 
               summarise(total = sum(anxiety_score), n =n()) %>%                
               mutate(avg = total/n),
             aes(program, avg, color = "Raw Survey Data")#Display the raw data for comparison
             ) +
  theme_light()+
  xlab("Program")+ ylab("Anxiety Score")+
  coord_flip()
```

@@

res_cgpa %>% 
  ggplot(aes(y = mean, x = fct_inorder(cgpa), color= "MRP estimate")) + 
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  geom_point(data = clean_data %>% 
               group_by(cgpa) %>% 
               summarise(total = sum(anxiety_score), n =n()) %>%                
               mutate(avg = total/n),
             aes(cgpa, avg, color = "Raw Survey Data")#Display the raw data for comparison
             ) +
  theme_light()+
  xlab("cgpa")+ ylab("Anxiety Score")+
  coord_flip()
```

@@

res_code %>% 
  ggplot(aes(y = mean, x = fct_inorder(coding_exp), color= "MRP estimate")) + 
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  geom_point(data = clean_data %>% 
               group_by(coding_exp) %>% 
               summarise(total = sum(anxiety_score), n =n()) %>%                
               mutate(avg = total/n),
             aes(coding_exp, avg, color = "Raw Survey Data")#Display the raw data for comparison
             ) +
  theme_light()+
  xlab("Coding Experience")+ ylab("Anxiety Score")
```

@@

# Appendix {-}
